
```{r, eval=FALSE}
unique(sapply(train, class)) # all variables are either numeric or integer

mylengths <- sapply(train, function(x) length(unique(x)))
mylengths[mylengths<20]
```

All of the data is read in as either numeric or integer data, but some of the variables have low cardinality, suggesting they might be better treated as nominal or ordinal data. Several features had only one value (*feat47*, *feat48*, *feat49*, *feat50*, and *feat51*). Since these do not provide any information about the target, I deleted them. 

```{r}
train[, feat47:=NULL]
train[, feat48:=NULL]
train[, feat49:=NULL]
train[, feat50:=NULL]
train[, feat51:=NULL]
```

I decided to treat any variable with a cardinality of 2 as a nominal variable and those with a cardinality of 10 or less as an ordinal variable. 

```{r}
train[, target:=factor(target)]
train[, feat4:=ordered(feat4)]
train[, feat8:=ordered(feat8)]
train[, feat12:=ordered(feat12)]
train[, feat16:=ordered(feat16)]
train[, feat17:=ordered(feat17)]
train[, feat29:=factor(feat29)]
train[, feat30:=factor(feat30)]
train[, feat31:=ordered(feat31)]
train[, feat35:=factor(feat35)]
train[, feat36:=factor(feat36)]
train[, feat43:=factor(feat43)]
train[, feat52:=factor(feat52)]
train[, feat55:=factor(feat55)]
train[, feat56:=ordered(feat56)]
train[, feat66:=ordered(feat66)]
train[, feat69:=ordered(feat69)]
train[, feat75:=ordered(feat75)]
train[, feat76:=ordered(feat76)]
```

The variables effected are summarized in the table below.
```{r, results='asis'}
mylengths <- sapply(train, function(x) length(unique(x)))

varsEffected <- names(train)[mylengths<10]
varsEffected <- varsEffected[varsEffected!='target']

mytable <- data.frame(Cardinality=mylengths[varsEffected])
mytable$Class <- with(mytable, ifelse(Cardinality==2, 'Nominal', 'Ordinal'))
library(pander)
pander(mytable, style='rmarkdown')
```

I noticed several variables that had a very large number of 0 values. It seems that a 0 value has some special significance for many of the variables.

The percentage of zeros in each variable is presented in Appendix 1.

```{r}
myzeros <- round(sapply(train, function(x) 100*sum(x==0)/length(x)), 1)
mytable <- data.frame(dat=paste0(myzeros, '%'))
mytable$dat <- as.character(mytable$dat)
mytable$dat[mytable$dat=='NA%'] <- 'N/A'
names(mytable) <- "% 0's"
row.names(mytable) <- names(myzeros)
write.csv(mytable, file='C:/Users/Robert/cloud/Classes/Data Prep/Final Project/Percent Zeros.csv')
```

I suspect that many of the variables are censored and 0 is used to represent "greater than the detection limit" or "less than the detection limit" or something similar. Censored data is a common phenomenon in biological data. Survival analysis typically deals with right censored data because the lifespan of organisms still living at the end of the study period is partially unknown. Analysis of chemical concentrations often deals with left censored data because when the concentration of a chemical drops below a certain point the lab can no longer detect it. 

Take for example a plot of **feat44**. This looks like a classic case of left-censored data. 

```{r}
ggplot(train, aes(x=feat44, fill=target))+
  geom_bar()
```


```{r}
# take only those where target=1
tmp <- train[target==0 & !is.na(feat44), list(exampleid, target, feat44)]
ggplot(tmp, aes(x=feat44, fill=target))+
  geom_bar()+
  ggtitle('Before Imputation')+
  guides(fill=F)

library(NADA)
test <- cenfit(obs=tmp[,feat44], censored=tmp[,feat44==0])
mymean <- mean(test)['mean'] # estimated mean
mymin <- tmp[feat44!=0, min(feat44)] # min with 0's removed
mydiff <- abs(mymean-mymin) # mean - min
myn <- sum(tmp$feat44==0) # how many values to bootstrap
mysamp <- sample(tmp[feat44>=(mymean+mydiff), feat44], myn, replace=T) # sample the right side of my distribution
myimp <- mymean-abs(mymean-mysamp) # flip sample values over the mean
tmp[, Ifeat44:=F]
tmp[feat44==0, Ifeat44:=T] # mark those I am about to replace with imputed values
tmp[feat44==0, feat44:=myimp] # replace 0's with values

ggplot(tmp, aes(x=feat44, fill=Ifeat44))+
  geom_bar()+
  geom_vline(xintercept=mymin)+
  ggtitle('After Imputation')+
  guides(fill=F)
```



The variables I consider possibly left censored are **feat10**, **feat34**, **feat44**, **feat46**, **feat59**, **feat60**, **feat65**, **feat73**, **feat77**

Those that are possibly right-censored are **feat26**, **feat27**, **feat28**, **feat45**, **feat53**, **feat54**, **feat61**, **feat67**, **feat78**, 

Some variables also look to be censored on both the left and right side. These are **feat3**, **feat68**, 

Others that may be censored in some other way are **feat11**, **feat13**, **feat14**, **feat15**, **feat20**, **feat21**, **feat37**, **feat38**, **feat39**, **feat40**, **feat41**, **feat42**, **feat62**, **feat63**, **feat72**, **feat74**

```{r}
ggplot(train, aes(x=feat26, fill=target))+
  geom_bar()

ggplot(train[feat3!=0, ], aes(x=feat3, fill=target))+
  geom_bar(binwidth=0.01)
```



