The first task is to impute the actual missing values. I employ regression trees to impute each of the missing variables.

```{r, cache=TRUE}
library(party)
library(survival)

traintmp <- train[, exampleid:=NULL]
mytree20 <- ctree(feat20~., data=traintmp[!is.na(feat20), ])
train[, Ifeat20:=feat20]
train[is.na(Ifeat20), Ifeat20:=predict(mytree20, newdata=train[is.na(feat20),])]

mytree21 <- ctree(feat21~., data=traintmp[!is.na(feat21), ])
train[, Ifeat21:=feat21]
train[is.na(Ifeat21), Ifeat21:=predict(mytree21, newdata=train[is.na(feat21),])]

mytree22 <- ctree(feat22~., data=traintmp[!is.na(feat22), ])
train[, Ifeat22:=is.na(feat22)]
train[is.na(feat22), feat22:=predict(mytree22, newdata=train[is.na(feat22),])]

library(reshape2)
tmp <- melt(train[!is.na(feat22), ], id.vars=c('exampleid', 'feat22'))
ggplot(tmp, aes(x=value, y=feat22, group=variable))+
  facet_wrap(~variable)+
  geom_smooth()
```


```{r}
# take only those where target=1
tmp <- train[target==0 & !is.na(feat44), list(exampleid, target, feat44)]
ggplot(tmp, aes(x=feat44, fill=(feat44==0)))+
  geom_bar()+
  ggtitle('Before Imputation')+
  guides(fill=F)

library(NADA)
test <- cenfit(obs=tmp[,feat44], censored=tmp[,feat44==0])
mymean <- mean(test)['mean'] # estimated mean
mymin <- tmp[feat44!=0, min(feat44)] # min with 0's removed
mydiff <- abs(mymean-mymin) # mean - min
myn <- sum(tmp$feat44==0) # how many values to bootstrap
mysamp <- sample(tmp[feat44>=(mymean+mydiff), feat44], myn, replace=T) # sample the right side of my distribution
myimp <- mymean-abs(mymean-mysamp) # flip sample values over the mean
tmp[, Ifeat44:=F]
tmp[feat44==0, Ifeat44:=T] # mark those I am about to replace with imputed values
tmp[feat44==0, feat44:=myimp] # replace 0's with values

ggplot(tmp, aes(x=feat44, fill=Ifeat44))+
  geom_bar()+
  geom_vline(xintercept=mymin)+
  ggtitle('After Imputation')+
  guides(fill=F)
```



The variables I consider possibly left censored are **feat10**, **feat34**, **feat44**, **feat46**, **feat59**, **feat60**, **feat65**, **feat73**, **feat77**

Those that are possibly right-censored are **feat26**, **feat27**, **feat28**, **feat45**, **feat53**, **feat54**, **feat61**, **feat67**, **feat78**, 

Some variables also look to be censored on both the left and right side. These are **feat3**, **feat68**, 

Others that may be censored in some other way are **feat11**, **feat13**, **feat14**, **feat15**, **feat20**, **feat21**, **feat37**, **feat38**, **feat39**, **feat40**, **feat41**, **feat42**, **feat62**, **feat63**, **feat72**, **feat74**
